\Huge Conferences in the Era of Expensive Carbon

### 2019-10-15 main.tex
Small
CP

\PARAGRAPH{Data gathering}
%
Beyond encouraging conferences to trim their emissions, public 
accounting will generate useful data for future organizers.  To this end,
emissions data should be published both in aggregate 
form (total and per-participant footprints), for quick reference, and in raw
form, with an anonymized record for each participant in each
conference, including their originating city.  The data should be made
available in 
a central place, in a uniform format.  Most
conferences' footprints will be dominated by participants' air travel, but the
data gathered should go beyond this to include air travel to in-person PC
meetings and estimated hotel and food {\COtwoE} footprints.

ACM should develop tools to gather and publicize this data. As a first step,
SIGPLAN recently built an air-travel-focused {\COtwoE} calculator for
conferences\iflater~\cite{carboncalculator}\bcp{Trim citation?  Is it even
 the right one? Link seems
 dead!  But Richard says ``As a reader, my first question is, how do I get
 access to this calculator? Can you cite this calculator in some way? It
 would be great to give a citation to where people can learn about it or
 use it, even if just, "To learn more about the calculator, e-mail xxx"''}\fi. 
Users can upload conference registration data, and the
calculator will estimate the {\COtwoE} cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other forms of conference emissions.

@@

While public accounting of {\COtwoE} expenditures will incentivize some 
reductions, it is not likely, by itself, to induce major changes.

@@

Science is a fundamentally social process, and the conference system
accelerates scientific research through high-bandwidth interaction,
direct dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to make changes that might
threaten these benefits.

>>>>

\PARAGRAPH{Data gathering}
%
Beyond encouraging conferences to trim their emissions, public 
accounting will generate useful data for future organizers.  
The data should be made
available in 
a central place, in a uniform format.  Most
conferences' footprints will be dominated by participants' air travel, but the
data gathered should go beyond this to include air travel to in-person PC
meetings and estimated hotel and food {\COtwoE} footprints.

ACM should develop tools to gather and publicize this data. 
SIGPLAN recently built an air-travel-focused {\COtwoE} calculator for
conferences\iflater~\cite{carboncalculator}\bcp{Trim citation?  Is it even
 the right one? Link seems
 dead!  But Richard says ``As a reader, my first question is, how do I get
 access to this calculator? Can you cite this calculator in some way? It
 would be great to give a citation to where people can learn about it or
 use it, even if just, "To learn more about the calculator, e-mail xxx"''}\fi. 
Users can upload conference registration data, and the
calculator will estimate the {\COtwoE} cost of air travel for those
sufficiently far away. This calculator could be expanded to account for
other forms of conference emissions.

@@

While public accounting of {\COtwoE} expenditures will incentivize some 
reductions, it is not likely, by itself, to induce major changes.
%
Science is a fundamentally social process, and the conference system
accelerates scientific research through high-bandwidth interaction,
direct dissemination of results, network building, and serendipitous
cross-fertilization.
%
Organizers and attendees will be reticent to make changes that might
threaten these benefits.

@@
